%-------------------------
% Resume in Latex
% Author : David Buckley
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/buckley-w-david}{\Large David Buckley}} & Email : \href{mailto:david@davidbuckley.ca}{david@davidbuckley.ca}\\
  \href{https://github.com/buckley-w-david}{https://github.com/buckley-w-david} & Mobile : +1-905-324-8365 \\
\end{tabular*}

%--------SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Python, Go, C, C\#, SQL,}
      \hfill
      \textbf{Technologies}{: Git, Docker, Kubernetes, AWS, Azure, GCloud}
    }
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Guelph}{Guelph, ON}
      {Bachelor of Computing;  GPA: 3.83}{Sept. 2014 -- April. 2019}
      \resumeItemListStart
        \resumeItem{Dr. Charles Capstick Graduation Prize}
          {Awarded to the students who have achieved the highest and second highest cumulative averages at graduation in the School of Computer Science.}
        \resumeItem{Dr. James Linders Scholarship}
          {Awarded to the student with the highest average in Year 3 Computing and Information Science core courses in Software Engineering.}
        \resumeItem{Dr. Ted Swart Scholarship}
          {Awarded to the student with the highest average in Year 2 Computing and Information Science core courses in Software Engineering.}
        \resumeItem{Dr. Mary McLeish Scholarship}
          {Awarded to the student with the highest average in Year 1 Computing and Information Science core courses in Software Engineering.}
        \resumeItem{Dean’s Honours List}
          {Awarded to students who have obtained a minimum semester average of 80.0\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {CARFAX Canada}{London, ON}
      {Junior Developer}{Fed 2020 - Current}
      \resumeItemListStart
        \resumeItem{Vehicle History Report - Redesign}
          {Re-implemented and redesigned the legacy VHR monolith from the ground up, converting it into a backend API and frontend website.

          This necessitated breaking the project into small pieces (Such as the registrations section of the report), carefully documenting the legacy implementation, and re-implementing it into the new API and website. With care, time, and persistence, the team worked through the entirety of the report this way, eventually completing the re-implementation and successfully launching the product.}
        \resumeItem{Vehicle History Report - Maintenance}
          {Implemented bug fixes and feature requests for legacy VHR product, such as correcting faulty data processing or leveraging unused data source to enhance existing sections of the report.}
        \resumeItem{Code Review}
          {Took part in code review (both giving and receiving) on pull requests for code changes in the course of the redesign and maintenance work.}
        \resumeItem{Documentation}
          {Documented code changes, both in terms of the what and why of them, but also the steps taken to ensure the implementation was correct (a combination of unit tests, integration tests, and manual spot checking).}
      \resumeItemListEnd

    \resumeSubheading
      {Canadian Digital Service}{Ottawa, ON}
      {Developer}{Jan 2018 - Sept 2018}
      \resumeItemListStart
        \resumeItem{NRCAN ETL}
          {Implemented the backend data processing and cleaning of nrcanapi.cds-snc.ca, a GraphQL API exposing National Resources Canada's EnerGuide housing data.}
        \resumeItem{Track web security compliance}
          {Worked with a small team to implement https-everywhere.canada.ca (not yet live). A service to track web security (such as HTTPS) compliance for Government of Canada websites.}
        \resumeItem{Continuous Integration and Deployment}
          {Using CircleCI, helped setup and maintain continuous integration and deployment configurations, as well as contributed to the test that the CI system ran.}
        \resumeItem{Code Review}
          {Performed code review on pull requests made by other team members.}
      \resumeItemListEnd

    \resumeSubheading
      {Cognitive Systems Corp.}{Waterloo, ON}
      {Software Developer/Cloud Analyst}{April 2017 - Sept 2017}
      \resumeItemListStart
        \resumeItem{Analysis Pipeline}
          {Using Apache Spark, Zookeeper, HDFS, and HBase via their Scala API, designed and implemented distributed data analysis applications to analyze information reported by IoT devices.}
        \resumeItem{Analysis API}
          {Designed and implemented web API to run and serve results of analysis jobs.}
        \resumeItem{Documentation}
          {Diagrammed and documented above systems via company wiki to explain use and guide future work on project.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
%\section{Projects}
%  \resumeSubHeadingListStart
%    \resumeSubItem{PROJECT}
%      {DESCRIPTION}
%  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
